Supplement: Analysis and code for 'Testing Perceptual Accuracy in Charts using Surveys

### 2023-07-13 analysis/analysis.qmd
link to data

library(readxl)
library(lubridate)
library(patchwork)
library(survey)
#library(ggmosaic)
library(ggpcp)
library(broom)
library(latex2exp)
library(gt) # grammar of tables
library(multcomp)

@@

vs_repo_local <- "~/Documents/projects/NORC" # link to local version of the visual_studies repo
```

@@

```{r data-1}
# other github repo. 
round1 <- readRDS(file.path(vs_repo_local, "visual-studies/data/round1.rds"))
round2 <- readRDS(file.path(vs_repo_local, "visual-studies/data/round2.rds"))

@@

```{r data-rnd6}
# other github repo. 
round6 <- readRDS(file.path(vs_repo_local, "visual-studies/data/round6.rds"))

@@

```{r data-rnd7}
# other github repo. 
round7 <- readRDS(file.path(vs_repo_local, "visual-studies/data/round7.rds"))

@@

This test is equivalent to a logistic regression with response $Y_{ij}$, the response of participant $i$  to question $Q_j$ $j = 1/2$ is correct (=1) or incorrect (=0):
$$
\text{logit } P \left(Y = 1 \mid Q_j \right) = \alpha + \beta_j, 
$$
We assume that $Y \mid Q_j$ has a Bernoulli distribution with success probability $p_j$, $j = 1, 2$. 
For the purpose of estimability, we will assume that $\beta_1 = 0$, i.e. $\text{logit} (p_1) = \alpha$ and $\beta_2 = \text{logit}(p_2) - \text{logit}(p_1)$. The odds of an accurate answer with aligned bars is therefore  exp (`r round(coefs_12$estimate[2],1)`) =  `r round(exp(coefs_12$estimate[2]),1)` times higher than for the unaligned bars of Question 1.

```{r}
coefs_12$term <- c("$$\\widehat{\\alpha}$$", "$$\\widehat{\\beta}_2$$")

>>>>

library(readxl)
library(lubridate)
library(patchwork)
library(survey)
#library(ggmosaic)
library(ggpcp)
library(broom)
library(latex2exp)
library(gt) # grammar of tables
library(multcomp)
library(here)

@@

vs_repo_local <- here::here("data") # link to the data folder (of the visual_studies repo)
```

@@

```{r data-1}
# other github repo. 
round1 <- readRDS(file.path(vs_repo_local, "round1.rds"))
round2 <- readRDS(file.path(vs_repo_local, "round2.rds"))

@@

```{r data-rnd6}
# other github repo. 
round6 <- readRDS(file.path(vs_repo_local, "round6.rds"))

@@

```{r data-rnd7}
# other github repo. 
round7 <- readRDS(file.path(vs_repo_local, "round7.rds"))

@@

This test is equivalent to a logistic regression with response $Y_{ij}$, the response of participant $i$  to question $Q_j$ $j = 1/2$ is correct (=1) or incorrect (=0):
$$
\text{logit } P \left(Y = 1 \mid Q_j \right) = \alpha + \beta_j, 
$$
We assume that $Y \mid Q_j$ has a Bernoulli distribution with success probability $p_j$, $j = 1, 2$. 
For the purpose of estimability, we will assume that $\beta_1 = 0$, i.e. $\text{logit} (p_1) = \alpha$ and $\beta_2 = \text{logit}(p_2) - \text{logit}(p_1)$. The odds of an accurate answer with aligned bars is therefore  exp (`r round(coefs_12$estimate[2],1)`) =  `r round(exp(coefs_12$estimate[2]),1)` times higher than for the unaligned bars of Question 1. Estimates for this model fit are shown in @tbl-coefs-12.

```{r}
#| label: tbl-coefs-12
#| tbl-cap: Estimates for the logit model of accuracy by task
coefs_12$term <- c("$$\\widehat{\\alpha}$$", "$$\\widehat{\\beta}_2$$")
